\newglossaryentry{ardrone}{
  name={AR.Drone},
  text={AR.Drone},
  description={A remote controlled flying quadcopter built by the French company Parrot.}
}

\newglossaryentry{python}{
  name={Python},
  text={Python},
  description={A high level general purpose computing language.}
}

\newglossaryentry{pygame}{
  name={Pygame},
  text={Pygame},
  description={A cross-platform set of \gls{python} modules designed for writing video games.}
}

\newglossaryentry{pyopengl}{
  name={PyOpenGL},
  text={PyOpenGL},
  description={A \gls{python} wrapper for \gls{opengl}.}
}

\newglossaryentry{pymc3}{
  name={PyMC3},
  text={PyMC3},
  description={An open-source  probabilistic programming framework for Python.}
}

\newglossaryentry{opengl}{
  name={OpenGL},
  text={OpenGL},
  description={A cross-language, cross-platform \gls{api} for rendering \gls{2d} and \gls{3d} vector graphics.}
}

\newglossaryentry{navlight}{
  name={navigation light},
  text={navigation light},
  description={Also known as a running light; coloured source of illumination on various vehicles which signal the craft's heading and status.}
}

\newglossaryentry{docker}{
  name={Docker},
  text={Docker},
  description={An open-source software project which automates the deployment of Linux applications inside software containers.}
}

\newglossaryentry{qt}{
  name={Qt},
  text={Qt},
  description={(pronounced ``cute'') A cross-platform application framework for developing application software}
}

\newglossaryentry{pyqt5}{
  name={PyQt5},
  text={PyQt5},
  description={A set of \gls{python} bindings for \gls{qt}.}
}

\newglossaryentry{rviz}{
  name={rviz},
  text={\textsf{rviz}},
  description={A \gls{3d} visualization tool for \gls{ros}.}
}

\newdualentry[longplural={unmanned aerial vehicles}]
	     [longplural={unmanned aerial vehicles}]
	     {uav}{UAV}{unmanned aerial vehicle} {
  A machine which flies in the air without carrying human passengers.
}

\newdualentry{ros}{ROS}{Robot Operating System} {
  An open-source collection of software frameworks for robot software development.
}

\newdualentry{best}{BEST}{Bayesian Estimation Supersedes the $t$ Test} {
  Bayesian estimation for two groups which provides complete distribution of credible values for the effect size, group means and their difference, standard deviations and their difference, and the normality of the data.
  By John K. Kurschke.
}

\newdualentry{slam}{SLAM}{Simultaneous Localization and Mapping} {
  Constructing or updating a map of an unknown environment while simultaneously keeping track of an agent's location within it.
}

\newdualentry[see={spir}]{spirit}{SPIRIT}{Subimposed Past Image Records Implemented for Teleoperation} {
  A method which enables operators to see a model of their robot with respect to its environment, in \gls{3d}.
}
\newdualentry{hpd}{HPD}{Highest Posterior Density interval} {
  The narrowest interval among all of the Bayesian credible intervals.
}

\newdualentry{ci}{CI} {
  Credible Interval}{An interval such that  the probability of a parameter lying in the interval is a certain value.
}

\newacronym{cg}{CG}{Computer Graphics model}
\newacronym{ip}{IP}{Internet Protocol}
\newacronym{api}{API}{Application Programming Interface}
\newacronym[longplural={fields of view}]{fov}{FOV}{field of view}
\newacronym{yaml}{YAML}{Yet Another Markup Language}
\newacronym{mocap}{mocap}{motion capture}
\newacronym{spir}{SPIR}{Teleoperation System Using Past Image Records}
\newacronym{kyodai}{KU}{Kyoto University}
\newacronym{ps3}{PS3}{PlayStation 3}
\newacronym[longplural={degrees of freedom}]{dof}{DOF}{degree of freedom}
\newacronym{lrf}{LRF}{laser rangefinder}
\newacronym{ai}{AI}{artificial intelligence}
\newacronym{imu}{IMU}{inertial measurement unit}
\newacronym{fpv}{FPV}{first person view}
\newacronym{aov}{AOV}{angle of view}
\newacronym{gui}{GUI}{graphical user interface}
\newacronym{ugv}{UGV}{unmanned ground vehicle}
\newacronym[see={slam}]{lsdslam}{LSD-SLAM}{Large-Scale Direct Monocular SLAM}
\newacronym{ptam}{PTAM}{Parallel Tracking and Mapping}
\newacronym[see={slam}]{rtslam}{RT-SLAM}{Real Time SLAM}
\newacronym{ekf}{EKF}{Extended Kalman Filter}
\newacronym{gps}{GPS}{Global Positioning System}
\newacronym{rf}{RF}{reference frame}
\newacronym[plural=DOSes, longplural={degradations of signal}]{dos}{DOS}{degradation of signal}
\newacronym[plural=LOSes, longplural={losses of signal}]{los}{LOS}{loss of signal}
\newacronym{rms}{RMS}{Root Mean Square}
\newacronym{rmse}{RMSE}{Root Mean Square Error}
\newacronym{nasa}{NASA}{National Aeronautics and Space Agency}
\newacronym{nasatlx}{NASA-TLX}{NASA Task Load Index}
\newacronym{tlx}{TLX}{Task Load Index}

\newacronym{mental}{MD}{Mental Demand}
\newacronym{physical}{PD}{Physical Demand}
\newacronym{temporal}{TD}{Temporal Demand}
\newacronym{performance}{P}{Performance}
\newacronym{effort}{E}{Effort}
\newacronym{frustration}{F}{Frustration}
\newacronym{tlxscore}{WS}{Weighted Score}

\newglossaryentry{2d} {
  name={2\textsc{d}},
  description={Two dimensional space.},
}

\newglossaryentry{3d} {
  name={3\textsc{d}},
  description={Three dimensional space.},
}


\newsymbol{rollaxis}{x_b}{roll axis}{Axis positive out of nose of the aircraft in the plane of symmetry of the aircraft}
\newsymbol{pitchaxis}{z_b}{pitch axis}{Axis perpendicular to the \gls{sym:rollaxis}, in the plane of symmetry of the aircraft, positive below the aircraft}
\newsymbol{yawaxis}{y_b}{yaw axis}{Axis perpendicular to the \glssymbol{sym:rollaxis}\glssymbol{sym:pitchaxis}-plane, positive out the right wing}

\newsymbol{roll}{\phi}{roll angle}{Rotation around the \gls{sym:rollaxis}}
\newsymbol{pitch}{\theta}{pitch angle}{Rotation around the \gls{sym:pitchaxis}}
\newsymbol{yaw}{\psi}{yaw angle}{Rotation around the \gls{sym:yawaxis}}

\newsymbol{pos}{\mathbf{x}}{position}{A position vector in \gls{3d}}
\newsymbol{posx}{x}{$x$-position}{The $x$-component of the position}
\newsymbol{posy}{y}{$y$-position}{The $y$-component of the position}
\newsymbol{posz}{z}{$z$-position}{The $z$-component of the position}

\newsymbol{quat}{\mathbf{q}}{quaternion}{A quaternion in \gls{3d}}
\newsymbol{quatim}{\mathbf{I}}{imaginary}{The imaginary components of a quaternion}
\newsymbol{quatx}{b}{$b$}{The $b$-component of $\glssymbol{sym:quat} = \glssymbol{sym:quatw} + \glssymbol{sym:quatx}\mathbf{i} + \glssymbol{sym:quaty}\mathbf{j} + \glssymbol{sym:quatz}\mathbf{k}$}
\newsymbol{quaty}{c}{$c$}{The $c$-component of $\glssymbol{sym:quat} = \glssymbol{sym:quatw} + \glssymbol{sym:quatx}\mathbf{i} + \glssymbol{sym:quaty}\mathbf{j} + \glssymbol{sym:quatz}\mathbf{k}$}
\newsymbol{quatz}{d}{$d$}{The $d$-component of $\glssymbol{sym:quat} = \glssymbol{sym:quatw} + \glssymbol{sym:quatx}\mathbf{i} + \glssymbol{sym:quaty}\mathbf{j} + \glssymbol{sym:quatz}\mathbf{k}$}
\newsymbol{quatw}{a}{$a$}{The $a$-component of $\glssymbol{sym:quat} = \glssymbol{sym:quatw} + \glssymbol{sym:quatx}\mathbf{i} + \glssymbol{sym:quaty}\mathbf{j} + \glssymbol{sym:quatz}\mathbf{k}$}

    
\newsymbol{state}{\mathbf{a}}{state vector}{A pose state vector containing the position and orientation}
\newsymbol{rotmat}{\mathbf{R}}{rotation matrix}{A rotation matrix}

\newsymbol{rfcurrent}{C}{current \acrshort{rf}}{The reference frame of the currently displayed frame}
\newsymbol{rfdrone}{D}{drone \acrshort{rf}}{The reference frame of the drone}
\newsymbol{rfprocessed}{F}{processing \acrshort{rf}}{The reference frame of the frame being processed}
\newsymbol{rfglobal}{G}{global \acrshort{rf}}{The reference frame of the global coordinate system}

\newsymbol{aov}{\alpha}{angle of view}{The angular extent of a given scene that is imaged by a camera}
\newsymbol{aovv}{\sym{aov}_v}{vertical \acrshort{aov}}{The angle of view in the vertical direction}
\newsymbol{aovh}{\sym{aov}_h}{horizontal \acrshort{aov}}{The angle of view in the horizontal direction}
\newsymbol{aovr}{\gamma}{aspect ratio}{The aspect ratio of a camera}

\newsymbol{evalfn}{E}{evaluation function}{An evaluation function, where $\sym{evalfn} = \Sigma\sym{coeff}_{\sym{elemidx}}\sym{elem}_{\sym{elemidx}}$}
\newsymbol{coeff}{k}{coefficient}{The coefficient of an element in an evaluation function}
\newsymbol{elem}{f}{element}{An element in an evaluation function}
\newsymbol{nelems}{n}{number of elements}{The number of elements in an evaluation function}
\newsymbol{elemidx}{i}{element index}{The index of an element in an evaluation function}

\newsymbol{rotang}{\theta}{rotation angle}{The angle by which an axis in the axis-angle representation is rotated}
\newsymbol{uvec}{\mathbf{e}}{rotation vector}{The vector around which the rotation happens in the axis-angle representation, in \gls{3d}}

\newsymbol{popsize}{N}{population size}{The total population size.}
\newsymbol{samplesize}{n}{sample size}{The size of the sample.}
\newsymbol{mean}{\mu}{mean}{The value obtained by dividing the sum of several quantities by their number; an average.}
\newsymbol{std}{\sigma}{standard deviation}{A quantity expressing by how much the members of a group differ from the mean value for the group.}
\newsymbol{effect}{g}{effect size}{Hedge's $g$ is an effect size used to indicate the standardised difference between two means.}

